---
output:
  github_document:
    html_preview: true
---

<!-- badges: start -->
  [![Codecov test coverage](https://codecov.io/gh/bcgov/bcgwlreports/branch/main/graph/badge.svg)](https://app.codecov.io/gh/bcgov/bcgwlreports?branch=main)
  <!-- badges: end -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# BC Groundwater Level Percentiles Report

[![img](https://img.shields.io/badge/Lifecycle-Maturing-007EC6)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)

This package creates reports of percentile classes of Provincial Groundwater Observation Well groundwater levels.

### Installation

To install the package from [GitHub](https://github.com/bcgov/bcgwlreports), use the [`remotes`](https://cran.r-project.org/package=remotes) package then the `bcgwlreports` package:

```{r, echo=TRUE, eval=FALSE}
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("bcgov/bcgwlreports")
```


### Usage

To use the bcgwlreports functions, the package must be first called from the library:

```{r, echo=TRUE, eval=FALSE}
library(bcgwlreports)
```

The following is an example of how to create and save an HTML report from a list of wells for the current date:

```{r, echo=TRUE, eval=FALSE}
# List some wells from the West Coast Region
wells <- c("OW204", "OW211", "OW312", "OW329", "OW351", "OW355", 
           "OW371", "OW383", "OW389", "OW437", "OW470")

# Give the report a title
report_title <- paste0("West Coast Region Groundwater Level Conditions")

# Give the report a description
report_description <- paste0("The following provides an overview of groundwater (GW) conditions ",
                             "in the West Coast Region as of ", format(Sys.Date(), format = "%B %d, %Y"), ".")

# Build the report
well_report (ows = wells,
             report_dates = c(Sys.Date()),
             title = report_title,
             description = report_description,
             n_days = 14,
             years_min = 5,
             out_dir = ".",
             name = "west_coast_region")
```

This report will calculate the percentiles of recent data compared to historical water levels. The report will look for data on the reporting date (`report_dates` argument) and will look back 14 days (`n_days` argument; will also look forward 14 days if a previous date selected). Minimum 5 years of level data is required to calculate a percentile (`years_min` argument). The title and description of the report need to be provided using the `title` and `description` arguments, and a directory folder and file name also need to be provided using the `out_dir` and `name` arguments.
More information on the `well_report` function can be found in the documentation `?well_report`.

Running the `well_report` function may take several minutes (up to 15-20 min if many) depending on the number of wells provided (to download and combine the information).


### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/groundwater-level-review-report/issues).

### How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in 
this project you agree to abide by its terms.

### License

```
Copyright 2022 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed
under the License is distributed on an &quot;AS IS&quot; BASIS, WITHOUT
WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied. See the License
for the specific language governing permissions and limitations under the
License.
```

---

This repository is maintained by the [Water Protection and Sustainability Branch](https://www2.gov.bc.ca/gov/content/environment/air-land-water/water) of the British Columbia Ministry of Land, Water and Resource Stewardship.
